Extended Formal Analysis of the EDHOC Protocol in Tamarin

### 2022-07-22 formalization.tex
[fix] remove editor's notes
[fix] grammatical and consistency fixes

On top of the standard Dolev-Yao model,~\cite{Norr21} allows the adversary to
access the long-term and ephemeral keys.
%
Long-term key reveal, denoted $\mRevLTK^{t}(A)$, stands for the adversary
gaining access to a party $A$'s long-term private key \mPriv{A} at a time point $t$.
%
Ephemeral key reveal, denoted $\mRevEph^{t}(A, k)$, stands for the adversary
obtaining, at time $t$, the ephemeral private key \mPrivE{A} used by party $A$
in a session where they establish key material $k$.
%
% Ephemeral keys might be stored in a less secure part of a device,
% but long-term keys are often stored and operate within a secure model,
% like a trusted execution environment (TEE). \vnote{Do we want to say more 
% about TEEs here?}
%
Formalizing these two capabilities allows more fine-grained control
over the access that an adversary has to these fundamentally different kinds of
keys.
%
Furthermore, we extend the results from~\cite{Norr21} by strengthening the
adversary capabilities, as detailed next.
%

@@

Users can extend the default term algebra and equational theory in
\mTamarin{} with new function symbols and unification rules for these new 
symbols.
%
For example, \mEdhoc{} requires authenticated encryption, which we model 
using
the symbol \mT{aeadEncrypt}.
%
We augment \mTamarin{} with the following rule for this operation,
which represents the fact that if the adversary knows a key \mT{k},
a message \mT{m}, and authenticated data \mT{ad},
and has access to an encryption algorithm \mT{ai},
then they can obtain the message corresponding to the authenticated 
encryption
of \mT{m} with \mT{k}~\cite{Norr21}.
%
{\footnotesize
\begin{verbatim}
[!KU(k), !KU(m), !KU(ad), !KU(ai)] --[]-> [!KU(aeadEncrypt(k, m, ad, ai))]
\end{verbatim}}
%
Other than modeling authenticated encryption, we use \mTamarin{}'s builtin
equational theories for signing, Diffie-Hellman, hashing and \mXor{}.
%

@@

In this work we consider the following properties: secrecy of the session key,
injective agreement and implicit agreement of the session key material for both
initiator and responder, and secrecy and integrity of the application data sent
on message 3 ($\mAD_3$)
%
Agreement is considered on a set of parameters $S$ which also contains the
session key material \mSessKey{}.
%
We will first describe in detail both properties, and then describe the
contents of the set $S$.
%
We formalize these properties as shown in Figure~\ref{fig:props}, which is
a modified version of a figure in~\cite{Norr21}.
\begin{figure*}[ht]
\begin{align*}
    \mPredPcs \triangleq\ & \forall \mTID, I, R, \mSessKey, t_2, t_3\mLogicDot
    \mK^{t_3}(\mSessKey)\  \land\ 
    (\mIComplete^{t_2}(\mTID, I, R, \mSessKey)\, \lor\, \mRComplete^{t_2}(\mTID, I, R, 
\mSessKey))
    \rightarrow\\
    &(\exists t_1\mLogicDot \mRevLTK^{t_1}(I) \land t_1 \lessdot t_2)
    \ \lor\ (\exists t_1\mLogicDot \mRevLTK^{t_1}(R) \land t_1 \lessdot t_2)\\
    &\ \lor\ (\exists t_1\mLogicDot \mRevEph^{t_1}(R, \mSessKey))
    \ \lor\ (\exists t_1\mLogicDot \mRevEph^{t_1}(I, \mSessKey))\\
    &\ \lor\ (\exists t_0, t_1\mLogicDot \mIStart^{t_0}(\mTID, I, R) \land \mTEE^{t_1}(R) \land (t_0 \lessdot t_1 \land t_1 \lessdot t_2))\\
    &\ \lor\ (\exists t_0, t_1\mLogicDot \mRStart^{t_0}(\mTID, R, \mSessKey, S) \land \mTEE^{t_1}(I) \land (t_0 \lessdot t_1 \land t_1 \lessdot t_2))\\[2em]
%
    \mPredInjI \triangleq\ &
    \forall \mTID_I, I, R, \mSessKey, S, t_2\mLogicDot \mIComplete^{t_2}(I, R, 
\mSessKey, S)
    \rightarrow\\
    &(\exists \mTID_R, t_1\mLogicDot \mRStart^{t_1}(\mTID_R, R, \mSessKey, S) \land t_1 \lessdot t_2
    \land (\forall \mTID_I', I', R', t_1' \mLogicDot \mIComplete^{t_1'}(\mTID_I', I' , R', \mSessKey, S)
        \rightarrow t_1' \doteq t_1))\\
    &\ \lor\ (\exists t_1\mLogicDot \mRevLTK^{t_1}(R) \land t_1 \lessdot t_2)\\
    &\ \lor\ (\exists t_0, t_1\mLogicDot \mIStart^{t_0}(\mTID_I, I, R) \land \mTEE^{t_1}(R) \land (t_0 \lessdot t_1 \land t_1 \lessdot t_2))\\[2em]
%
    \mPredInjR \triangleq\ &
    \forall \mTID_R, I, R, \mSessKey, S, t_2\mLogicDot \mRComplete^{t_2}(\mTID_R, I, R, 
\mSessKey, S)
    \rightarrow\\
    &(\exists \mTID_I, t_1\mLogicDot \mIStart^{t_1}(\mTID_I, I, R, \mSessKey, S) \land t_1 \lessdot t_2
    \land (\forall \mTID_R', I' R' t_1' \mLogicDot \mRComplete^{t_1'}(\mTID_R', I' , R', \mSessKey, S)
        \rightarrow t_1' \doteq t_1))\\
    &\ \lor\ (\exists t_1\mLogicDot \mRevLTK^{t_1}(I) \land t_1 \lessdot t_2)\\
    &\ \lor\ (\exists t_0, t_1\mLogicDot \mRStart^{t_0}(\mTID_R, R, \mSessKey, S) \land \mTEE^{t_1}(I) \land (t_0 \lessdot t_1 \land t_1 \lessdot t_2))\\[2em]
%
    \mPredImpI \triangleq\ &
    \forall \mTID_I, I, R, \mSessKey, S, t_1\mLogicDot \mIComplete^{t_1}(\mTID_I, I, R, \mSessKey, 
S)
    \rightarrow\\
      &(\forall \mTID_R, I', R', S', t_2\mLogicDot \mRComplete^{t_2}(\mTID_R, I', R', \mSessKey, S') \rightarrow
             (I=I' \land R=R' \land S=S')\\
      &\ \ \land (\forall \mTID_I', I', R', S', t_1'\mLogicDot
        \mIComplete^{t_1'}(\mTID_I', I', R', \mSessKey, S') \rightarrow t_1' \doteq t_1
        ))\\
    &\lor(\exists t_0\mLogicDot \mRevLTK^{t_0}(R) \land t_0 \lessdot t_1)
    \lor(\exists t_0\mLogicDot \mRevEph^{t_0}(R, \mSessKey))
    \lor(\exists t_0\mLogicDot \mRevEph^{t_0}(I, \mSessKey))\\
    &\lor\ (\exists t_0, t_1\mLogicDot \mIStart^{t_0}(\mTID_I, I, R) \land \mTEE^{t_1}(R) \land (t_0 \lessdot t_1 \land t_1 \lessdot t_2))
\end{align*}
%
\caption{Formalization of security properties and adversary model.}
\label{fig:props}
\end{figure*}

%----------------------------------------------------------------------- PFS
\subsubsection{Secrecy of the session key material.}
\label{sec:secrecy}
We show that the adversary cannot gain access to the session key material \mSessKey{},
even under a weak post-compromise security model that allows the adversary limited access
to the long-term keys of the parties involved through a secure interface before the session starts, 
unrestricted access to the long-term keys of the involved parties after the session ends
and of all other parties, as well as access to all other session keys.
%
This property is formalized as \mPredPcs{}
in Figure~\ref{fig:props}.
%

In the \mIComplete{} event, \mTID{} represents a ``thread identifier'' for the
current session, $I$ represents the identity of the initiator,
and $R$ represents the identity of the party who the initiator believes is
playing the responder role, while \mSessKey{} stands for the established
session key material.
%
\mRComplete{} has analogous parameters; in particular, the responder $R$
believes $I$ is the party playing the initiator role.
%
Intuitively, the PCS property states that an adversary obtains \mSessKey{}
only if one of the following conditions hold: either a party's long-term key
is compromised before their run ends, or \mSessKey{} is directly revealed to
the attacker, or the TEE interface for the responder is used during the current
session for the initiator (i.e. after the initiator starts and before it
commits), or, similarly, the TEE interface for the initiator is used during the
current session for the responder.
%
The property in Figure~\ref{fig:props} is unlike the actual \mTamarin{} lemma
in one minor way: \mTamarin's logic does not allow disjunctions to appear on
the left-hand side of an implication inside a universally-quantified formula.
%
Therefore, in the \mTamarin{} code, instead of using the disjunction
$\mIComplete^{t_2}(\mTID, I, R, \mSessKey)\, \lor\, 
\mRComplete^{t_2}(\mTID, I, R, \mSessKey)$
to model the fact that either party may have completed their execution, we use
a single action parametrized by the terms $\mTID$, $I$, $R$, and \mSessKey.

%-------------------------------------------------------------------- InjAgree
\subsubsection{Authentication Properties.}
\label{sec:authenticationDef}
Following~\cite{Norr21}, we prove two different kinds of authentication
properties, namely \emph{injective agreement} in the style
of~\cite{DBLP:conf/csfw/Lowe97a}, and implicit agreement.
%
Injective agreement can be guaranteed to either party running the protocol.
%
For the initiator $I$, it guarantees to $I$ that whenever $I$ believes that
they have completed a run with $R$ as responder, then the party $R$ has 
indeed
executed the protocol in the role of a responder, and that this run of $I$
uniquely corresponds to one of $R$ where the set of parameters is $S$ and
includes, in particular, the session key material \mSessKey{}.
%
It can be defined for $R$ in a similar manner.

@@

The ``implicit'' in the name of the property stands for the fact that a party
$A$ assumes that any party $B$ who has access to the session key material
\mSessKey{} must, in fact, be the intended party, and that if $B$ is honest,
$B$ will agree on a set $S$ of parameters which includes \mSessKey.
%
Implicit agreement for both roles guarantees to $A$ that $A$ is or has been
involved in exactly one protocol execution with $B$, and that $B$ agrees or
will agree with $A$ on $S$.
%
This property diverges from injective agreement in that upon sending
the last message, $A$ concludes that if this message reaches $B$, then $A$
and $B$ agree on each other's identities and roles, and the set $S$.
%

Note that for implicit agreement to hold for $I$, the ephemeral keys must not
be revealed since the property relies on the fact that the intended responder
is the only one who knows the session key material.
%
If the adversary has access to the ephemeral keys, they can use them along 
with
the public keys of $I$ and $R$ to compute the session key material.
%
However, either party's long-term key can be revealed after the other
party has finished their execution, since this still leaves the adversary
unable to compute \mGxy{}.
%

@@

%------------------------------------------------------- Agreed parameters
\subsubsection{Parameters in set $S$.}
\label{sec:agreedParams}
We now describe the set $S$ of parameters upon which the two parties obtain
guarantees via the above properties.
%
The initiator $I$ gets injective and implicit agreement guarantees on the
following partial set $S_P$ of parameters~\cite{Norr21}:
\begin{itemize}
    \item the roles played by itself and its peer,
    \item responder identity,
    \item session key material (which varies depending on the \mEdhoc{} 
method),
    \item context identifiers \mCi{} and \mCr{}, and
    \item cipher suites \mSuites{}.
\end{itemize}
%

Due to the initiator being guaranteed identity protection under \mEdhoc{}, $I$
cannot get explicit agreement with $R$ on the initiator's identity.
%
Similarly, when using the \mStat{} authentication method, $I$ does not get 
any
such guarantees about $P_{I}$.
%
However, $I$ does get implicit agreement with $R$ about $I$'s identity and the
full set $S_{F}$ of agreed parameters.
%
In contrast, since $R$'s run finishes after that of $I$, $R$ can get explicit
injective agreement assurances on the full set $S_{F}$ of agreed parameters.
%
The full set of agreed parameters $S_F$ is $S_P \cup \{I, P_I\}$ when $P_I$
is part of the session key material, and $S_P \cup \{I\}$ otherwise.
%

In addition to these properties, a couple of properties can be inferred
without being explicitly modelled and verified.
%
One such property is Key-Compromise Impersonation
(KCI)~\cite{DBLP:conf/ima/Blake-WilsonJM97}.
%
A KCI attack occurs when an adversary who has access to $A$'s long-term 
private
key to make $A$ believe that they completed an execution with a peer $B$,
while $B$ did not participate in said execution at all.
%
This is in particular relevant when \mStat{} authentication methods are used.
%
Our above notions of agreement ensure that both parties agree on each
other's identity, role, and session key material.
%
Therefore, all \mEdhoc{} methods that satisfy these agreement properties also
avoid KCI attacks.
%

Another kind of attack is Unknown Key Share attacks
(UKS)~\cite{DBLP:conf/ima/Blake-WilsonJM97}.
%
As part of a UKS attack, a party $A$ can be made to believe that it finished
an execution with a party $B$, but where the session key material is actually
shared between $A$ and $C$ instead.
%
Again, due to the agreement on identities and session key material, any 
method
that satisfies the above agreement properties also resists UKS attacks.
%
Overall, the agreement properties capture entity authentication,
and satisfy any properties based on that notion.
%
However, see Section~\ref{sec:unintendedPeerAuth} for a discussion on the
interaction between \mEdhoc{} and the application leading to similar issues.
%

@@

As mentioned earlier, we use actions to represent parametrized events.
%
For example, in line 27 above, the action
\verb|ExpRunningR(~tid, $V, exp_sk, agreed)| represents an event of type
\mRStart{} parametrized by the session id, the responder's identity, and the
session key material \mT{exp\_sk}.
%
The \mT{exp} in the name of the variable for session key material represents
the fact that the agreement property satisfied by this key is explicit, i.e.,
it includes $P_{I}$, as in Section~\ref{sec:agreedParams}.
%
We use \mT{imp\_sk} for the corresponding session key material which does 
not
include $P_{I}$.
%
For the \mSigSig{} and \mSigStat{} methods, therefore, the two values are the 
same.
%

>>>>

On top of the standard Dolev-Yao model,~\cite{Norr21} allows the adversary to
access the long-term and ephemeral keys.
%
Long-term key reveal, denoted $\mRevLTK^{t}(A)$, stands for the adversary
gaining access to a party $A$'s long-term private key \mPriv{A} at a time point $t$.
%
Ephemeral key reveal, denoted $\mRevEph^{t}(A, k)$, stands for the adversary
obtaining, at time $t$, the ephemeral private key \mPrivE{A} used by party $A$
in a session where they establish key material $k$.
%
Formalizing these two capabilities allows more fine-grained control
over the access that an adversary has to these fundamentally different kinds of
keys.
%
Furthermore, we extend the results from~\cite{Norr21} by strengthening the
adversary capabilities, as detailed next.
%

@@

Users can extend the default term algebra and equational theory in
\mTamarin{} with new function symbols and unification rules for these new 
symbols.
%
For example, \mEdhoc{} requires authenticated encryption, which we model 
using
the symbol \mT{aeadEncrypt}.
%
We augment \mTamarin{} with the following rule for this operation,
which represents the fact that if the adversary knows a key \mT{k},
a message \mT{m}, and authenticated data \mT{ad},
and has access to an encryption algorithm \mT{ai},
then they can obtain the message corresponding to the authenticated 
encryption
of \mT{m} with \mT{k}~\cite{Norr21}.
%
{\footnotesize
\begin{verbatim}
[!KU(k), !KU(m), !KU(ad), !KU(ai)] --[]-> [!KU(aeadEncrypt(k, m, ad, ai))]
\end{verbatim}}
%
Other than modeling authenticated encryption, we use \mTamarin{}'s built-in
equational theories for signing, Diffie-Hellman, hashing and \mXor{}.
%

@@

In this work we consider the following properties: secrecy of the session key,
injective agreement and implicit agreement of the session-key material for both
initiator and responder, and secrecy and integrity of the application data sent
on message 3 ($\mAD_3$)
%
Agreement is considered on a set of parameters $S$ which also contains the
session-key material \mSessKey{}.
%
We will first describe in detail both properties, and then describe the
contents of the set $S$.
%
We formalize these properties as shown in Figure~\ref{fig:props}, which is
a modified version of a figure in~\cite{Norr21}.
\begin{figure*}[ht]
\begin{align*}
    \mPredPcs \triangleq\ & \forall \mTID, I, R, \mSessKey, t_2, t_3\mLogicDot
    \mK^{t_3}(\mSessKey)\  \land\ 
    (\mIComplete^{t_2}(\mTID, I, R, \mSessKey)\, \lor\, \mRComplete^{t_2}(\mTID, I, R, 
\mSessKey))
    \rightarrow\\
    &(\exists t_1\mLogicDot \mRevLTK^{t_1}(I) \land t_1 \lessdot t_2)
    \ \lor\ (\exists t_1\mLogicDot \mRevLTK^{t_1}(R) \land t_1 \lessdot t_2)\\
    &\ \lor\ (\exists t_1\mLogicDot \mRevEph^{t_1}(R, \mSessKey))
    \ \lor\ (\exists t_1\mLogicDot \mRevEph^{t_1}(I, \mSessKey))\\
    &\ \lor\ (\exists t_0, t_1\mLogicDot \mIStart^{t_0}(\mTID, I, R) \land \mTEE^{t_1}(R) \land (t_0 \lessdot t_1 \land t_1 \lessdot t_2))\\
    &\ \lor\ (\exists t_0, t_1\mLogicDot \mRStart^{t_0}(\mTID, R, \mSessKey, S) \land \mTEE^{t_1}(I) \land (t_0 \lessdot t_1 \land t_1 \lessdot t_2))\\[2em]
%
    \mPredInjI \triangleq\ &
    \forall \mTID_I, I, R, \mSessKey, S, t_2\mLogicDot \mIComplete^{t_2}(I, R, 
\mSessKey, S)
    \rightarrow\\
    &(\exists \mTID_R, t_1\mLogicDot \mRStart^{t_1}(\mTID_R, R, \mSessKey, S) \land t_1 \lessdot t_2
    \land (\forall \mTID_I', I', R', t_1' \mLogicDot \mIComplete^{t_1'}(\mTID_I', I' , R', \mSessKey, S)
        \rightarrow t_1' \doteq t_1))\\
    &\ \lor\ (\exists t_1\mLogicDot \mRevLTK^{t_1}(R) \land t_1 \lessdot t_2)\\
    &\ \lor\ (\exists t_0, t_1\mLogicDot \mIStart^{t_0}(\mTID_I, I, R) \land \mTEE^{t_1}(R) \land (t_0 \lessdot t_1 \land t_1 \lessdot t_2))\\[2em]
%
    \mPredInjR \triangleq\ &
    \forall \mTID_R, I, R, \mSessKey, S, t_2\mLogicDot \mRComplete^{t_2}(\mTID_R, I, R, 
\mSessKey, S)
    \rightarrow\\
    &(\exists \mTID_I, t_1\mLogicDot \mIStart^{t_1}(\mTID_I, I, R, \mSessKey, S) \land t_1 \lessdot t_2
    \land (\forall \mTID_R', I' R' t_1' \mLogicDot \mRComplete^{t_1'}(\mTID_R', I' , R', \mSessKey, S)
        \rightarrow t_1' \doteq t_1))\\
    &\ \lor\ (\exists t_1\mLogicDot \mRevLTK^{t_1}(I) \land t_1 \lessdot t_2)\\
    &\ \lor\ (\exists t_0, t_1\mLogicDot \mRStart^{t_0}(\mTID_R, R, \mSessKey, S) \land \mTEE^{t_1}(I) \land (t_0 \lessdot t_1 \land t_1 \lessdot t_2))\\[2em]
%
    \mPredImpI \triangleq\ &
    \forall \mTID_I, I, R, \mSessKey, S, t_1\mLogicDot \mIComplete^{t_1}(\mTID_I, I, R, \mSessKey, 
S)
    \rightarrow\\
      &(\forall \mTID_R, I', R', S', t_2\mLogicDot \mRComplete^{t_2}(\mTID_R, I', R', \mSessKey, S') \rightarrow
             (I=I' \land R=R' \land S=S')\\
      &\ \ \land (\forall \mTID_I', I', R', S', t_1'\mLogicDot
        \mIComplete^{t_1'}(\mTID_I', I', R', \mSessKey, S') \rightarrow t_1' \doteq t_1
        ))\\
    &\lor(\exists t_0\mLogicDot \mRevLTK^{t_0}(R) \land t_0 \lessdot t_1)
    \lor(\exists t_0\mLogicDot \mRevEph^{t_0}(R, \mSessKey))
    \lor(\exists t_0\mLogicDot \mRevEph^{t_0}(I, \mSessKey))\\
    &\lor\ (\exists t_0, t_1\mLogicDot \mIStart^{t_0}(\mTID_I, I, R) \land \mTEE^{t_1}(R) \land (t_0 \lessdot t_1 \land t_1 \lessdot t_2))
\end{align*}
%
\caption{Formalization of security properties and adversary model.}
\label{fig:props}
\end{figure*}

%----------------------------------------------------------------------- PFS
\subsubsection{Secrecy of the Session-key Material.}
\label{sec:secrecy}
We show that the adversary cannot gain access to the session-key material
\mSessKey{}, even under a weak post-compromise security model that allows the
adversary limited access to the long-term keys of the parties involved through a
secure interface before the session starts, unrestricted access to the long-term
keys of the involved parties after the session ends and of all other parties, as
well as access to all other session keys.
%
This property is formalized as \mPredPcs{} in Figure~\ref{fig:props}.
%

In the \mIComplete{} event, \mTID{} represents a ``thread identifier'' for the
current session, $I$ represents the identity of the initiator,
and $R$ represents the identity of the party who the initiator believes is
playing the responder role, while \mSessKey{} stands for the established
session-key material.
%
\mRComplete{} has analogous parameters; in particular, the responder $R$
believes $I$ is the party playing the initiator role.
%
Intuitively, the PCS property states that an adversary obtains \mSessKey{}
only if one of the following conditions hold: either a party's long-term key
is compromised before their run ends, or \mSessKey{} is directly revealed to
the attacker, or the TEE interface for the responder is used during the current
session for the initiator, i.e., after the initiator starts and before it
commits, or, similarly, the TEE interface for the initiator is used during the
current session for the responder.
%
The property in Figure~\ref{fig:props} is unlike the actual \mTamarin{} lemma
in one minor way: \mTamarin's logic does not allow disjunctions to appear on
the left-hand side of an implication inside a universally-quantified formula.
%
Therefore, in the \mTamarin{} code, instead of using the disjunction
$\mIComplete^{t_2}(\mTID, I, R, \mSessKey)\, \lor\,
\mRComplete^{t_2}(\mTID, I, R, \mSessKey)$
to model the fact that either party may have completed their execution, we use
a single action parametrized by the terms $\mTID$, $I$, $R$, and \mSessKey.

%-------------------------------------------------------------------- InjAgree
\subsubsection{Authentication Properties.}
\label{sec:authenticationDef}
Following~\cite{Norr21}, we prove two different kinds of authentication
properties, namely \emph{injective agreement} in the style
of~\cite{DBLP:conf/csfw/Lowe97a}, and implicit agreement.
%
Injective agreement can be guaranteed to either party running the protocol.
%
For the initiator $I$, it guarantees to $I$ that whenever $I$ believes that
they have completed a run with $R$ as responder, then the party $R$ has 
indeed
executed the protocol in the role of a responder, and that this run of $I$
uniquely corresponds to one of $R$ where the set of parameters is $S$ and
includes, in particular, the session-key material \mSessKey{}.
%
It can be defined for $R$ in a similar manner.

@@

The ``implicit'' in the name of the property stands for the fact that a party
$A$ assumes that any party $B$ who has access to the session-key material
\mSessKey{} must, in fact, be the intended party, and that if $B$ is honest,
$B$ will agree on a set $S$ of parameters which includes \mSessKey.
%
Implicit agreement for both roles guarantees to $A$ that $A$ is or has been
involved in exactly one protocol execution with $B$, and that $B$ agrees or
will agree with $A$ on $S$.
%
This property diverges from injective agreement in that upon sending
the last message, $A$ concludes that if this message reaches $B$, then $A$
and $B$ agree on each other's identities and roles, and the set $S$.
%

Note that for implicit agreement to hold for $I$, the ephemeral keys must not
be revealed since the property relies on the fact that the intended responder
is the only one who knows the session-key material.
%
If the adversary has access to the ephemeral keys, they can use them along 
with
the public keys of $I$ and $R$ to compute the session-key material.
%
However, either party's long-term key can be revealed after the other
party has finished their execution, since this still leaves the adversary
unable to compute \mGxy{}.
%

@@

%------------------------------------------------------- Agreed parameters
\subsubsection{Parameters in set $S$.}
\label{sec:agreedParams}
We now describe the set $S$ of parameters upon which the two parties obtain
guarantees via the above properties.
%
The initiator $I$ gets injective and implicit agreement guarantees on the
following partial set $S_P$ of parameters~\cite{Norr21}:
\begin{itemize}
    \item the roles played by itself and its peer,
    \item responder identity,
    \item session-key material (which varies depending on the \mEdhoc{} 
method),
    \item context identifiers \mCi{} and \mCr{}, and
    \item cipher suites \mSuites{}.
\end{itemize}
%

Due to the initiator being guaranteed identity protection under \mEdhoc{}, $I$
cannot get explicit agreement with $R$ on the initiator's identity.
%
Similarly, when using the \mStat{} authentication method, $I$ does not get 
any
such guarantees about $P_{I}$.
%
However, $I$ does get implicit agreement with $R$ about $I$'s identity and the
full set $S_{F}$ of agreed parameters.
%
In contrast, since $R$'s run finishes after that of $I$, $R$ can get explicit
injective agreement assurances on the full set $S_{F}$ of agreed parameters.
%
The full set of agreed parameters $S_F$ is $S_P \cup \{I, P_I\}$ when $P_I$
is part of the session-key material, and $S_P \cup \{I\}$ otherwise.
%

In addition to these properties, a couple of properties can be inferred
without being explicitly modelled and verified.
%
One such property is Key-Compromise Impersonation
(KCI)~\cite{DBLP:conf/ima/Blake-WilsonJM97}.
%
A KCI attack occurs when an adversary who has access to $A$'s long-term 
private
key to make $A$ believe that they completed an execution with a peer $B$,
while $B$ did not participate in said execution at all.
%
This is in particular relevant when \mStat{} authentication methods are used.
%
Our above notions of agreement ensure that both parties agree on each
other's identity, role, and session-key material.
%
Therefore, all \mEdhoc{} methods that satisfy these agreement properties also
avoid KCI attacks.
%

Another kind of attack is Unknown Key Share attacks
(UKS)~\cite{DBLP:conf/ima/Blake-WilsonJM97}.
%
As part of a UKS attack, a party $A$ can be made to believe that it finished
an execution with a party $B$, but where the session-key material is actually
shared between $A$ and $C$ instead.
%
Again, due to the agreement on identities and session-key material, any 
method
that satisfies the above agreement properties also resists UKS attacks.
%
Overall, the agreement properties capture entity authentication,
and satisfy any properties based on that notion.
%
However, see Section~\ref{sec:unintendedPeerAuth} for a discussion on the
interaction between \mEdhoc{} and the application leading to similar issues.
%

@@

As mentioned earlier, we use actions to represent parametrized events.
%
For example, in line 27 above, the action
\verb|ExpRunningR(~tid, $V, exp_sk, agreed)| represents an event of type
\mRStart{} parametrized by the session id, the responder's identity, and the
session-key material \mT{exp\_sk}.
%
The \mT{exp} in the name of the variable for session-key material represents
the fact that the agreement property satisfied by this key is explicit, i.e.,
it includes $P_{I}$, as in Section~\ref{sec:agreedParams}.
%
We use \mT{imp\_sk} for the corresponding session-key material which does not
include $P_{I}$.
%
For the \mSigSig{} and \mSigStat{} methods, therefore, the two values are the
same.
%
